---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
tutorial_options(exercise.timelimit = 1e6)
```

```{r setup, include=FALSE}
library(learnr)

```


# TCGA Data

### Exercise 

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE}

```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}

attachData('bcTCGA')
set.seed(1)   # Not necessary, but your CV results might look different than mine with a different seed

# Model fitting and CV
cvfit <- cv.glmnet(X, y)
fit <- cvfit$glmnet.fit
xlim <- log(c(fit$lambda[1], cvfit$lambda.min))
plot(fit, xlim=xlim, xvar="lambda")
plot(cvfit)

## lam values
max(fit$lambda)
cvfit$lambda.min
cvfit$lambda.1se

## R^2
max(1-cvfit$cvm/var(y))

## coef
b <- coef(cvfit)
b[which(b > 0.15),,drop=FALSE]

## coef (cont'd)
b <- coef(fit, s=0.2)
sum(b != 0)
b[which(b!=0),,drop=FALSE]

## predict
predict(cvfit, X[85,,drop=FALSE])
sapply(predict(fit, type="nonzero"), length)

# Slides 5-6
Fig2.10(cvfit)

# AIC/BIC (Slide 8)
fit1 <- ncvreg(X, y, penalty='lasso', lambda=cvfit$lambda)
fit2 <- ncvreg(X, y, penalty='lasso', lambda.min=0.001)
Fig2.11(fit1)
Fig2.11(fit2)

# AICc
Fig2.11_aicc <- function(fit, ...) {
  lam <- log(fit$lambda)
  ll <- logLik(fit)
  df <- pmin(as.numeric(attr(ll, "df")), fit$n-1)
  print(range(df))
  IC <- cbind(AIC(fit), BIC(fit), AIC(fit) + 2 * df * (df + 1)/(fit$n - df - 1))
  matplot(lam, IC, xlim = rev(range(lam)), col = hdrm:::pal(3), type = "l", 
          lwd = 3, lty = 1, bty = "n", xlab = expression(lambda), 
          xaxt = "n", las = 1, ylab = "AIC/BIC", ...)
  at <- seq(max(lam), min(lam), length = 5)
  axis(1, at = at, labels = round(exp(at), 2))
  hdrm:::toplegend(legend = c("AIC", "BIC", "AICc"), col = hdrm:::pal(3), lwd = 3)
}
Fig2.11_aicc(fit1)
Fig2.11_aicc(fit2, ylim=c(-100, 2000))
```

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

